Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-19 draft.tex
add math specification in props 2 and 3, clarify assumption on war lottery

For probabilities $p_1$ of outright victory and $1-p_1$ of loss, player $i \in \{s, g\}$ in period $t$ with a fixed cost of war $\zeta_i$ faces war lottery $\omega_{it} \equiv (p_1 (W_{it}-\zeta_i), \left(1-p_1\right)( L_{it}-\zeta_i))$. $\Omega_t \equiv (\omega_{gt}, \omega_{st}).$\footnote{Baseline costs of war are fixed ($\zeta_i$) but additional costs of war based on war's result are captured in $W_i$ and $L_i$.} Players are assumed to approach war lotteries as expected values.

@@

The strategies for the insides actors are the following, organized according to the patron's investments in each relevant state variable. In period $t$:

@@

\begin{proposition}
Assume the restrictions of \emph{Definition 1} hold in the absence of sanctions and that sanctions affect only player $s$'s payoffs to maintaining the Status Quo. In order for sanctions to lead to ceding by the secessionists, the following are required:

@@

\begin{proposition}
Assume the restrictions of \emph{Definition 1} hold in the absence of sanctions and that sanctions affect both player $s$'s status quo payoffs and its military capabilities. The parameter space over which a war will be initiated by the home state is increasing in the magnitude of the sanctions' impact on the secessionists' military capabilities.

>>>>

For probabilities $p_1$ of outright victory and $1-p_1$ of loss, player $i \in \{s, g\}$ in period $t$ with a fixed cost of war $\zeta_i$ faces war lottery $\omega_{it} \equiv (p_1 (W_{it}-\zeta_i), \left(1-p_1\right)( L_{it}-\zeta_i))$. $\Omega_t \equiv (\omega_{gt}, \omega_{st}).$\footnote{Baseline costs of war are fixed ($\zeta_i$) but additional costs of war based on war's result are captured in $W_i$ and $L_i$. Note that the structure of the war lottery along with the assumption that the outside actors influence the payoffs only and not the probabilities of winning imply that any way in which the patron influences the payoffs from war can be counteracted by the international community through its own investments.} Players are assumed to approach war lotteries as expected values.

@@

The strategies for the inside actors are the following, organized according to the patron's investments in each relevant state variable. In period $t$:

@@

\begin{proposition}
Assume the restrictions of \emph{Definition 1} hold in the absence of sanctions and that sanctions affect only player $s$'s payoffs to maintaining the Status Quo (i.e. $q_{s,t+1} = Q_{s,t} - \mu -\sigma$ where $\sigma$ is the reduction due to sanctions).  In order for sanctions to lead to ceding by the secessionists, the following are required:

@@

\begin{proposition}
Assume the restrictions of \emph{Definition 1} hold in the absence of sanctions and that sanctions affect both player $s$'s status quo payoffs and its military capabilities (i.e. $q_{s,t+1} = Q_{s,t} - \mu -\sigma$ \emph{and} $p_{1s}\left(\sigma\right)$ $\left(p_{1g}\left(\sigma\right)\right)$ is decreasing (increasing) in $\sigma$). The parameter space over which a war will be initiated by the home state is increasing in the magnitude of the sanctions' impact on the secessionists' military capabilities.
\end{proposition}
